### 2017-10-27 Risk analysis/Text/Layout/Layout/chapter2_methods.tex
Trap figures inserted

        \subsection{Hydrocarbon reservoir system and structural traps}
        Such hydrocarbon systems are typically comprised of:
        \begin{enumerate}
        	\item A kerogen-rich \textbf{source rock} which produced and emitted hydrocarbons during its burial history, given sufficient heating \citep{dolson2016basics} These are typically organic-rich sedimentary rocks, shales in particular. For the purpose of this work, it is assumed that a  suitable source rock is present and hydrocarbons expulsion took place after the formation of any trap-defining structures in our geological models.
        	\item A \textbf{pathway} that allows expelled oil and gas to migrate upwards through the subsurface from the source rock into potential reservoir formations \citep{dolson2016basics}. This condition is also assumed to be given in our model. Basement formations in the geological model are simply defined as permeable.
        	\item \textbf{Seal} formations that are able to halt hydrocarbons on their migration pathway. Such sealing is generally defined by a reduction of pore space geometry relative to migration energy. Lithologically, seals are most commonly comprised of shales, siltstones, tight carbonates, evaporites and salts. Sealing is thus defined primarily by changes in stratigraphical composition to low porosities and micro-sized pore throats, which are characterized by a high capillary entry pressure \citep{dolson2016basics, dolson2016quantifying}. An additional factor to sealing is posed by the presence of faults. Fault zones may possess significantly higher or lower permeabilities then surrounding rock formations which means that they may serve as fluid flow conduits or migration barriers or respectively \citep{van2003lateral, sorkhabi2005place}. The possible influence of faults on structural hydrocarbon traps is elaborated in further detail below. For the model in this work, the reservoir cap rock is assumed to be a shale.
        	\item Suitable \textbf{reservoir formations}, in which these hydrocarbons volumes can be stored. For this, a suitable percentage of void space in a rock formation, i.e. a sufficiently high porosity, is required. A second significant factor is the connectivity of the porosity through pore throats. The larger the pore throats, the easier it is for fluids to migrate in a rock. Typical reservoir rocks are sandstones and carbonates, but even normally tight lithologies might serve as reservoirs, if they are fractured \citep{dolson2016basics}. In the models of this work, reservoir formations are assumed to be conventional sandstones.
        \end{enumerate}
        Given the migration and a combination of appropriate reservoir-seal sequence geometries, many different types of traps, in which hydrocarbons can accumulate, are possible. A common trap type is a structural four-way closure, i.e. as reservoir-seal system that was folded into closed anticlines, often resembling a dome and is thus predominantly defined by the structural closure relief and the cap rock sealing capacity. Such a trap type can be considered to be closed, as the reservoir surface contours are closed in a circle or oval around a relief high. Closure can also defined by any other intersection of a contour with a seal. The point at which a a contour fails to close is referred to as spill point \citep{dolson2016basics}.

>>>>

        \subsection{Hydrocarbon reservoir system and structural traps}
        Such hydrocarbon systems are typically comprised of:
        	\item A kerogen-rich \textbf{source rock} which produced and emitted hydrocarbons during its burial history, given sufficient heating \citep{dolson2016basics} These are typically organic-rich sedimentary rocks, shales in particular. For the purpose of this work, it is assumed that a  suitable source rock is present and hydrocarbons expulsion took place after the formation of any trap-defining structures in our geological models.
        	\item A \textbf{pathway} that allows expelled oil and gas to migrate upwards through the subsurface from the source rock into potential reservoir formations \citep{dolson2016basics}. This condition is also assumed to be given in our model. Basement formations in the geological model are simply defined as permeable.
        	\item \textbf{Seal} formations that are able to halt hydrocarbons on their migration pathway as top, lateral and possibly bottom seals \citep{dolson2016basics, sorkhabi2005place}. Such sealing is generally defined by a reduction of pore space geometry relative to migration energy. Sealing is thus defined primarily by changes in stratigraphical composition to low porosities and micro-sized pore throats.These are characterized by a high capillary entry pressure able to resist the buoyancy pressure of hydrocarbons. Lithologically, seals are most commonly comprised of shales, siltstones, tight carbonates, evaporites and salts \citep{dolson2016basics, sorkhabi2005place, dolson2016quantifying}. An additional factor to sealing is posed by the presence of faults. Fault zones may possess significantly higher or lower permeabilities then surrounding rock formations which means that they may serve as fluid flow conduits or migration barriers respectively \citep{van2003lateral, sorkhabi2005place}. The possible influence of faults on structural hydrocarbon traps is elaborated in further detail below. For the model in this work, the reservoir cap rock is assumed to be a shale.
        	\item Suitable \textbf{reservoir formations}, in which these hydrocarbons volumes can be stored. For this, a suitable percentage of void space in a rock formation, i.e. a sufficiently high porosity, is required. A second significant factor is the connectivity of the porosity through pore throats. The larger the pore throats, the easier it is for fluids to migrate in a rock. Typical reservoir rocks are sandstones and carbonates, but even normally tight lithologies might serve as reservoirs, if they are fractured \citep{dolson2016basics}. In the models of this work, reservoir formations are assumed to be conventional sandstones.
        Given the migration and a combination of appropriate reservoir-seal sequence geometries, many different types of traps, in which hydrocarbons can accumulate, are possible. A common trap type is a structural four-way closure, i.e. as reservoir-seal system that was folded into closed anticlines, often resembling a dome and is thus predominantly defined by the structural closure relief and the cap rock sealing capacity. Such a trap type can be considered to be closed, as the reservoir surface contours are closed in a circle or oval around a relief high. Such closure can also be given through any other crossing of a structural contour with a seal, including faults. A point at which a contour fails to close is referred to as "spill point" \citep{dolson2016basics}.
        	\includegraphics[width=0.95\textwidth]{Figures/trap_closure.png}
        	\caption{Conceptual examples of a dome-shaped four-way-closure and a simple fault trap from top view (relief countour) and cross section perspective (modified from \citet{dolson2016basics}.)}
        The influence of faults and fault sealing potential on structural traps has been outlined by several researches such as \citet{sorkhabi2005place} and \citet{van2003lateral}.
			\begin{subfigure}{.8\textwidth}
				\includegraphics[width=1\linewidth]{Figures/fault_trap_mechA.png}
				%\caption{Graph and saddle point of the function $z=x2~-~y2$.}\label{fig:saddle_point} 
			\begin{subfigure}{0.18\textwidth}
				\includegraphics[width=1\linewidth]{Figures/fault_trap_mechB.png}
				%\caption{Saddle point between two maxima.}\label{fig:saddle_point_between_maxima} 
			\caption{Bla}\label{fig:fault_trap_spills}
